A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-12-09 doc/review-acom/stokes-eig.tex
update quadrature rule order discussion

As noted in~\cite{zhao2015robust}, integral
equation based methods provide several advantages.
%
Because the BIE is defined on the
boundary alone, there is a reduction in the
dimension of the domain to be discretized.
%
{\color{red}This reduces the number of required unknowns over finite
element discretizations. Further, it is known
that standard finite element approaches suffer from
high-frequency ``pollution'' in two and three dimensions
for oscillatory problems and, hence, the computation
of larger eigenvalues. In the original context, 
the term pollution refers to the fact that,
when solving the Helmholtz equation in dimension
greater than one,
the accuracy of the Galerkin solution of
a problem does indeed differ by a constant factor from
the error in the best approximation of the true
solution in the finite element space but this factor
{\it grows} as a function of the frequency $k$
\cite{babuska1997pollution}.
Thus, at higher frequencies, a finite element method
requires more degrees of freedom than suggested
by the number of degrees of freedom required to
resolve the solution.
In constrast, a BIE does not suffer from this
effect.}

@@

The integral kernels of the single and
double layer potentials have weak
singularities of the form $|\xx-\yy|^p\log |\xx-\yy|$
for some $p \in \N_0$, which require special
quadrature rules to achieve high-order accuracy.
%
In the examples below, we use generalized
Gaussian quadrature (GGQ)~\cite{bremer2010}.
%
To demonstrate the idea, we consider
evaluating the convolution of a kernel
$K$ with a density $\sigma$
at the boundary node $\xx_j(t_l)$.
%
GGQ is a Nystr\"{o}m-type discretization ---
the density is approximated 
by its values at the discretization nodes,
which we denote by
$\sigma_{qp} := \sigma(\xx_q(t_p))$.
%
The basis of a GGQ rule is a set of 
support nodes and weights for the
contribution to the integral from the
``self'' panel (panel $j$) and the adjacent
panels (with index in $A(j)$).
%

For the self panel, there is a special set
of nodes and weights for each interpolation
point. Denote the nodes and weights
for interpolation point $l$ by $t^{(l)}_{n}$
and $w^{(l)}_{n}$, respectively, with
$1\leq l \leq 16$ and $1\leq n \leq N_s$.
%
The adjacent panels are handled by a single
set of over-sampled support nodes and weights.
We denote these nodes and weights
by $\tilde{t}_n$ and $\tilde{w}_n$, respectively,
for $1 \leq n \leq N_a$.
%
For the 20th-order rule we used, $N_s = 16$ and
$N_a = 48$. 
%
The contribution of other panels is assumed
to be given to high accuracy by the standard
Gauss-Legendre weights, which we denote
by $w_n$.
%
Adding these contributions together, we obtain the
quadrature

@@

  The overall order of accuracy of the GGQ we use
  is 20th-order, up to the precision of the ``far''
  interactions.
\end{remark}

@@

\subsubsection{Convergence study}
\label{subsec:convannulus}
We demonstrate that 
for sufficiently large $N$, if $k_{0}$ is a Dirichlet 
eigenvalue of the annulus, 
then $f_{D}^{N}(k_{D}) = 0$ and $f_{C}^{N}(k_{C}) = 0$
where $|k_{D} - k_{0}| \lesssim N^{-20}$, 
and $|k_{C} - k_{0}| \lesssim N^{-20}$.
Recall that the GGQ we use has an expected order
of convergence of $N^{-20}$ for evaluating convolutions
with such integral kernels,
so that the error of the roots is observed to have the
same order as the quadrature rule.
In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$
and plot the errors $|k_{D}-k_{0}|$ and $|k_{C}-k_{0}|$ as a function
of $N$.

>>>>

As noted in~\cite{zhao2015robust}, integral
equation based methods provide several advantages.
%
Because the BIE is defined on the
boundary alone, there is a reduction in the
dimension of the domain to be discretized.
%
{\color{red}This reduces the number of required unknowns over finite
element discretizations. Further, it is known
that standard finite element approaches suffer from
high-frequency ``pollution'' in two and three dimensions
for oscillatory problems and, hence, the computation
of larger eigenvalues. In the original context,
pollution refers to the following phenomenon.
When solving the Helmholtz equation in dimension
greater than one,
the accuracy of the Galerkin solution of
a problem is indeed optimal in the sense that it
differs by a constant factor from
the error in the best approximation of the true
solution in the finite element space.
But this factor
{\it grows} as a function of the frequency $k$
\cite{babuska1997pollution}.
Thus, at higher frequencies, a finite element method
requires more degrees of freedom than suggested
by the number of degrees of freedom required to
resolve the solution.
In constrast, a standard BIE discretization does not
suffer from this effect.}

@@

The integral kernels of the single and
double layer potentials have weak
singularities of the form $|\xx-\yy|^{2p}\log |\xx-\yy|$
for some $p \in \N_0$, which require special
quadrature rules to achieve high-order accuracy.
%
In the examples below, we use generalized
Gaussian quadrature (GGQ)~\cite{bremer2010}.
%
To demonstrate the idea, we consider
evaluating the convolution of a kernel
$K$ with a density $\sigma$
at the boundary node $\xx_j(t_l)$.
%
GGQ is a Nystr\"{o}m-type discretization ---
the density is approximated 
by its values at the discretization nodes,
which we denote by
$\sigma_{qp} := \sigma(\xx_q(t_p))$.
%
The basis of a GGQ rule is a set of 
support nodes and weights for the
contribution to the integral from the
``self'' panel (panel $j$) and the adjacent
panels (with index in $A(j)$).
%

For the self panel, there is a special set
of nodes and weights for each interpolation
point. Denote the nodes and weights
for interpolation point $l$ by $t^{(l)}_{n}$
and $w^{(l)}_{n}$, respectively, with
$1\leq l \leq 16$ and $1\leq n \leq N_s$.
%
The adjacent panels are handled by a single
set of over-sampled support nodes and weights.
We denote these nodes and weights
by $\tilde{t}_n$ and $\tilde{w}_n$, respectively,
for $1 \leq n \leq N_a$.
%
For the {\color{red} 16th-order} rule we used
{\color{red} (i.e. a rule which integrates
  $p(\yy)\log|\xx-\yy| + q(\yy)$ for $p$ and $q$
  polynomials of degree up to 15)}, $N_s = 16$ and
  $N_a = 48$. 
%
The contribution of other panels is assumed
to be given to high accuracy by the standard
Gauss-Legendre weights, which we denote
by $w_n$.
%
Adding these contributions together, we obtain the
quadrature

@@

  The overall order of accuracy of the GGQ we use
  is {\color{red}16th-order}, up to the precision of the ``far''
  interactions.
\end{remark}

@@

\subsubsection{Convergence study}
\label{subsec:convannulus}
We demonstrate that 
for sufficiently large $N$, if $k_{0}$ is a Dirichlet 
eigenvalue of the annulus, 
then $f_{D}^{N}(k_{D}) = 0$ and $f_{C}^{N}(k_{C}) = 0$
where $|k_{D} - k_{0}| \lesssim N^{-20}$, 
and $|k_{C} - k_{0}| \lesssim N^{-20}$.
Recall that the GGQ we use {\color{red} is designed to
evaluate integrals of the form $p(\yy)\log|\xx-\yy|
+ q(\yy)$ with $p$ and $q$ polynomials of degree up
to 15, so that the observed convergence rate
for the roots is of slightly higher order than the
order of the quadrature rule. In our experience, the $N^{-20}$
rate is common for these kernels and may be a result of the
fact that the singularity for these kernels is of the form
$|\xx-\yy|^2\log|\xx-\yy|$, which is smoother than
$\log|\xx-\yy|$ itself.}
In~\cref{fig:conv}, we show this result for $k_{0} = 13.48025717955055$
and plot the errors $|k_{D}-k_{0}|$ and $|k_{C}-k_{0}|$ as a function
of $N$.
